\documentclass[12pt]{cv_style}
\usepackage{marvosym}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{fontawesome}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\font\titlefont=cmss12 at 36pt

%% Personal Information %%
\info{Lyndon Chan}{647-330-1294}{lyndon.chan@mail.utoronto.ca}{lyndonchan.github.io}{github.com/lyndonchan}

%% Education %%
\sectionheading{Education}
\flushleft\desc{M.A.Sc., Electrical Engineering (Communications Group)}{2017-present}{University of Toronto}{Toronto, Ontario, CANADA}
\begin{ditem}
	\item \textsc{Advisors:} Drs. Konstantinos Plataniotis \& Parham Aarabi
	\item \textsc{Thesis Topic:} \textit{Weakly-Supervised Semantic Segmentation in the Multi-Class Setting Across Different Image Domains}
	\item \textsc{Research Milestones:}
	\begin{ditem}
		\item \textsc{ICCV 2019} (Mar. 2019): \emph{HistoSegNet: Semantic Segmentation of Histological Tissue Type
in Whole Slide Images} (accepted)
		\item \textsc{CVPR 2019} (Nov. 2018): \emph{Atlas of Digital Pathology: A Generalized Hierarchical Histological Tissue Type-Annotated Database for Deep Learning} (\href{http://openaccess.thecvf.com/content_CVPR_2019/html/Hosseini_Atlas_of_Digital_Pathology_A_Generalized_Hierarchical_Histological_Tissue_Type-Annotated_CVPR_2019_paper.html}{paper})
		\item \textsc{IEEE TMI} (Nov. 2018): \emph{Focus Quality Assessment of High-Throughput Whole Slide Imaging in Digital Pathology} (\href{https://arxiv.org/abs/1811.06038}{paper})
		\item \textsc{2018 EngSci Machine Intelligence Bootcamp} (Sep. 2018): poster on \emph{Automated Abnormality Detection in Histopathological Images with Deep Learning}
	\end{ditem}
\end{ditem}
\medspace
\desc{B.A.Sc., Electrical Engineering (GPA 3.64 / 4.0, 17th of 129)}{2012-2017}{University of Toronto}{Toronto, Ontario, CANADA}
\begin{ditem}
	\item \textsc{Focus Areas:} "Control, Communications \& Signal Processing", "Analog \& Digital Electronics", "Software"
	\item \textsc{Capstone Project:} \textit{DARI: Depth-variable Augmented Reality Interface}	
\end{ditem}

%% Skills %%
\sectionheading{Skills}
\begin{ditem}
	\item \textbf{Programming Languages (most to least proficient):} Python (Keras, TensorFlow, Caffe), MATLAB, C/C++, Java, Ruby, R
	\item \textbf{Software:} \LaTeX, Windows Shell, Wiki Markup, Jupyter Notebook (in progress)
	\item \textbf{Languages:} English (native), Cantonese (fluent), Mandarin (conversational)
\end{ditem}

%% Interests %%
\sectionheading{Interests}
\begin{ditem}
	\item \textsc{Research Interests:} Weakly-Supervised Semantic Segmentation (WSSS), Computer-aided Diagnosis (CADx), Computer Vision, Intelligence Amplification (IA), Abnormality Detection
	\item \textsc{Other Interests:} Coding useful tools, Podcasting, Blogging, Teaching, Reading (history, philosophy), Music, Cooking, Translation, Hiking, Running, Swimming
\end{ditem}

\newpage
%% Research %%
\sectionheading{Research}
\desc{Master's Student Research Assistant}{Sep. 2017-present}{University of Toronto (Multimedia Lab)}{Toronto, Ontario, CANADA}
\textsc{Supervisors:} Drs. Konstantinos Plataniotis \& Parham Aarabi
\begin{ditem}
	\item Developing weakly-supervised semantic segmentation for histological tissue type in digital pathology, with future extensions to abnormality detection, image retrieval, and visual attention aid
	\item Drafted a study of mathematical derivations of CNN forward and backpropagation
	\item Performed histological tissue type annotations for digital pathology to build deep learning dataset
	\item Administers lab research meetings, interviewed prospective summer student researchers
\end{ditem}

%
\desc{Undergraduate Student Research Assistant}{May 2017-Aug. 2017}{University of Toronto (Multimedia Lab)}{Toronto, Ontario, CANADA}
\textsc{Supervisors:} Mahdi S. Hosseini, Dr. Konstantinos Plataniotis
\begin{ditem}
	\item Devised novel image recognition method using a network of fixed convolutional kernels with maximally-polynomial frequency response
\end{ditem}
%
\desc{Interim Engineering Intern}{May 2015-Aug. 2016}{Qualcomm Canada}{Markham, Ontario, CANADA}
\begin{ditem}
	\item Software development: built regression test frameworks for optical flow, cadence detection, deinterlacing, image compression
	\item Other work: performed subjective image quality assessment, administered and operated camera calibration lab \& mechanical camera testbed, competed in two internal Qualcomm HackMobile hackathons
\end{ditem}
%
\desc{Undergraduate Visiting Research Intern}{Jun.-Aug. 2014}{Hong Kong University of Science and Technology (Human Language Technology Centre)}{\\Clear Water Bay, New Territories, HONG KONG}
\textsc{Supervisors:} SU Dan, Dr. Pascale Fung
\begin{ditem}
	\item (1) Unsupervised clustering of user personalities by nationality from OkCupid
	\item (2) Song popularity prediction from user mentions on Sina Weibo posts
\end{ditem}
%
%\desc{High School Summer Research Assistant}{Jul.-Aug. 2012}{Sunnybrook Research Institute (Focused Ultrasound Group)}{Toronto, Ontario, CANADA}
%\textsc{Supervisors:} Mathew Carias, Dr. Kullervo Hynynen
%\begin{ditem}
	%\item Built and optimized ultrasound transducer catheters for therapeutic cardiac ablation through destructive testing
%\end{ditem}

%% Teaching %%
\sectionheading{Teaching}
\desc{ECE462: Multimedia Systems (Head Lab TA)}{Jan.-Apr. 2018}{University of Toronto}{Toronto, Ontario, CANADA}
\textsc{Instructor:} Dr. Dimitrios Hatzinakos\\
\begin{ditem}
	\item Responsible for designing and marking eight lab assignments and four quizzes, compiled student material for CEAB
\end{ditem}

%% Publications %%
%\sectionheading{Publications}
%\begin{ditem}
	%\item
%\end{ditem}
%
\end{document}